---
output: word_document
bibliography: references.bib
csl: jacc.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message=FALSE, error=FALSE, warning=FALSE, comment=NA, echo = knitr::is_html_output())   

```

```{r packages}
library("rms")
library("survival")
library("survminer")
library("here")
library("tidyverse")
library("patchwork")
               
theme_set(bayesplot::theme_default(base_family = "sans"))
savefigs <- TRUE

```

**Title**:

Bayesian Reanalysis Highlights Increased Mortality upon Pacemaker Exposure in Post-TAVR Patients 

**Running Title**:

Pacemaker Risk Following Transcatheter Aortic Valve Replacement

**Authors**:

Arthur M. Albuquerque

School of Medicine, Universidade Federal do Rio de Janeiro, Brazil

James M. Brophy

McGill Health University Center, Canada

**Conflicts of Interest Disclosures**:

Both authors do not report any potential conflicts of interest.

**Funding**:

JMB is a research scholar supported by Les Fonds de Recherche Québec Santé which had no influence on the choice of topic, the results, or conclusions. 

**Word Count**:

...

\newpage

**Structured Abstract**: (250 words)

Objectives:

Background:

Methods:

Results:

Conclusions:

**Key Words**: (3-5)

**Condensed Abstract**: (100 words)

\newpage

# Text

## Introduction

Recently, a nationwide Swedish, population-based cohort study found no
statistically significant difference for all-cause mortality (hazard ratio [HR] 1.03; 95% CI: 0.88 - 1.22; P = 0.692) in patients who underwent permanent pacemaker implantation after transcatheter aortic valve replacement (TAVR) between 2008 and
2018 [@RN5758]. Leading the authors to conclude that long-term survival
between patients who did and did not undergo permanent pacemaker
implantation after TAVR was not different. While the study included a
large unselected sample of 3,420 TAVR patients, there are a number of
reasons why it is of interest to query the strength of the evidence
supporting their conclusion. 

First, their central Kaplan--Meier curve shows survival curves crossing,
raising the possibility of a time-varying HR such that the proportional
hazards assumptions underlying their analysis may not be valid. Second
given this is an elderly population (mean age \> 81), the performed
comparative lifetime analysis with some patients followed up to 10
years may not be the most informative and clinically relevant. As
eventually, we all die and this analysis perhaps obscures some earlier
clinically pertinent mortality differences among those receiving and not
receiving pacemakers post-TAVR. Thirdly, the same nationwide databases
have examined the mortality impact of pacemaker implantation in a
contemporary population of aortic stenosis patients undergoing surgical
aortic valve replacement (SAVR) [@RN5759] and the inclusion of all or
some of this additional evidence may be informative. 

A Bayesian analysis [@RN4985] directly estimates the probability of
increased mortality post pacemaker insertion and which allows the
incorporation of past knowledge may be helpful in furthering our
understanding of this data by presenting actionable probabilities.

## Methods

### Data source

To gain approximate access to this dataset, we digitalized the reported
Kaplan--Meier mortality curve in the propensity score-matched cohort [@RN5758]. We extracted this data instead of from the full cohort since propensity score matching yields more balanced comparative groups than the crude data. This was operationalized by
following the technique of Guyot [@RN5762], utilizing
the website WebPlotDigitalizer and the R
programming language [@R]. Specifically, this reconstruction of the
individual patient data used the R package IPDfromKM [@IPDfromKM] thereby
allowing secondary Bayesian survival analyses to be performed. 

### Outcome

While the original publication examined several different outcomes, this
analysis is limited to the main outcome of total mortality as that is
the only outcome for which we can estimate Kaplan--Meier-derived
individual patient data (IPD). Given that the median follow-up is 2.7
years, that the KM slopes appear to change beyond 4 years and that
assessing the impact of pacemaker implantation seems clinically most
relevant in this shorter time window, we prespecified a maximum 4 year
follow-up.


### Statistical analyses

Bayesian approaches to survival analysis can provide a number of
benefits over the classical frequentist approach, including the ability
to make direct probability statements about parameters of interest (the
risk of pacemaker implantation), and to incorporate prior knowledge. These probability statements arise from the posterior distribution according to the following equation [@mcelreath2020]:     
 $$ Posterior\:  = \frac{\text{Probability of the data} * Prior}{\text{Average probability of the data}} $$

Therefore, in addition to the current data summarized by the probability of the data (likelihood) one requires a prior probability distribution each parameter. The robustness of the Bayesian approach is often assessed by sensitivity analyses that examine the variation in the posterior probability as a function of the choice of different prior distributions.  

The mechanics of the Bayesian analyses were performed using the Stan programming
language [@stan] through the R package 
rstanarm [@rstanarm] . We fitted a proportional hazard regression model using cubic M-splines for the baseline hazard. Bayesian analyses require a prior distribution for each parameter. In this model, parameters were the intercept, M-spline coefficients, and coefficient regarding pacemaker exposure. Because our focus in this article was on the latter, we used rstanarm's default priors for the intercept and M-spline coefficients (Normal[0, 20] and Dirichlet[1, 1, 1, ...], respectively) in all analyses. To estimate pacemaker exposure's marginal posterior distribution, we used two different priors. First we performed the analysis using the rstanarm built-in default vague normal prior (Normal [0, 2.5]).  This prior places very little information into the model and it is completely dominated by the data. Next we used an informative prior
based on a previous study, using the same national databases, of pacemaker risk in a
cohort undergoing surgical aortic valve replacement (SAVR) [@RN5759]. We downweighted the influence of this informative prior by 50%, because while the populations are similar (everyone has aortic stenosis), the aortic valve interventions were different and the long term evolutions of SAVR patients receiving pacemakers may not be identical to TAVR patients. To downweight, we multiplied the original standard error by 1.5.

Marginal posterior distributions are summarized with medians and 95% highest-density intervals (credible intervals), defined as the narrowest interval containing 95% of the probability density function [@mcelreath2020]. 

All analyses were executed within the integrated development environment
of RStudio and the statistical code can be found on
Github (https://github.com/brophyj/tavr_pace). 

## Results

### Verifying individual data extraction

```{r load 8 years data}
# load the complete digitalized KM datasets
load(here::here("output/data/both_ipd8.RData"))
```

```{r frequentist cox}
# Fit Cox
cox <- survival::coxph(survival::Surv(time, status) ~ 1 + treat,
                       data = both_ipd8)

tidy_cox = 
  broom::tidy(cox, conf.int = T, exponentiate = T) %>% 
  select(-1) %>% 
  round(2)

```

Quality assessment of our Kaplan--Meier-derived IPD data extraction was
performed analytically by comparing our extracted overall hazard ratio and 95%
CI with the published values, and graphically by checking the derived Kaplan--Meier curves (Figure
1) with the published propensity-matched KM curve (Original
Supplemental Figure 2). Not only is the data extraction judged to be
adequate graphically but also numerically with a calculated HR = `r tidy_cox$estimate`,
95% CI `r tidy_cox$conf.low` - `r tidy_cox$conf.high` which compares favorably with the published value (HR: 0.99; 95% CI: 0.81 - 1.21).


```{r fig1, fig.height=5, fig.width=5.5, include=FALSE}

fig1 <- survminer::ggsurvplot(
    fit = survival::survfit(survival::Surv(time, status) ~ 1 + treat,
                            data = both_ipd8), 
    censor = F,
    xlab = "Time (years)", 
    ylab = "Cumulative Survival",
    conf.int = FALSE,
    xlim = c(0,8),
    ylim = c(0, 1),
    color = "strata",
    palette = c("black", "#EA3324"),
    risk.table = TRUE,
    risk.table.col = "strata", # Risk table color by groups
    legend.labs = c("No pacemaker", "Pacemaker"),    # Change legend labels
    risk.table.height = 0.3,
    legend.title = " ") 

# Suppress code used to save figure

# tiff(file = here::here("output", "figures", 
#                       'fig1.tif'),
#     height=14, width=18.1, units = "cm", res = 1200)
# 
# print(fig1, newpage = FALSE)
# 
# dev.off()

```

```{r diagnostics cox}

cox.zph <- survival::cox.zph(cox)  

# survminer::ggcoxzph(cox.zph)
# survminer::ggcoxdiagnostics(cox, type = "deviance", linear.predictions = FALSE)
```


The difference in survival probabilities with the 95% CI is plotted in
Figure 2. One of the concerns with the original analysis was the
possibility of time-varying proportional hazards which are again
suggested in this Figure. However, statistical tests suggested the
proportional hazards assumption was not violated (p = `r round(cox.zph$table[1,3],2)`), although it
bears mentioning that the power to detect violations with this sample
size is limited [@Austin].

```{r fig2 output, fig.width=5.5, fig.height=4, include=FALSE}
f <- rms::npsurv(survival::Surv(time, status) ~ 1 + treat,
                            data = both_ipd8)


# Suppress code used to save figure

# tiff(file = here::here("output", "figures", 
#                       'fig2.tif'),
#     height=14, width=20.1, units = "cm", res = 1200)
# 
# par(mar= c(4.2,6,2,3)) 


fig2 <- rms::survdiffplot(f,
                          order=2:1, # "Pacemaker" minus "No pacemaker"
                          time.inc=1,
                          conf.int = 0.95,
                          conf="shaded",
                          xlab = "Time (years)")


# dev.off()
```

### Standard survival analysis to 4 years

```{r load 4 years data}
# load the 4-years digitalized KM datasets
load(here::here("output/data/both_ipd4.RData"))
```

```{r cox 4 years}

# Fit Cox for 4 year data
cox4 <- survival::coxph(survival::Surv(time, status) ~ 1 + treat,
                       data = both_ipd4)

tidy_cox4 = 
  broom::tidy(cox4, conf.int = T, exponentiate = T) %>% 
  select(-1) %>% 
  round(2)

```

Even if the proportional hazards assumptions are not violated,
clinically it is indicated to investigate the risks over a more
restricted time window. In accordance also with the varying risks, we
elected a priori to concentrate on a 4-year time window. Using this time
frame, we extracted the individual data as described in the Methods section
above. The frequentist Cox proportional hazards model analysis for this
more restricted data set results in a HR = `r tidy_cox4$estimate`, 95% CI `r tidy_cox4$conf.low` - `r tidy_cox4$conf.high`, p =
`r tidy_cox4$p.value`. While this remains statistically not significant, the point
estimate has clearly moved towards a survival benefit in the no
pacemaker group. Using this analysis to conclude that a pacemaker does
not influence 4-year mortality risks makes the common error of confusing absence of
evidence with evidence of absence. To further explore the data, we
next performed a Bayesian survival analysis. 

### Bayesian surival analysis

```{r load bayesian models}

# Posteriors
load(here::here("output/fit/bayesian_model_vague.RData"))
load(here::here("output/fit/bayesian_model_informative.RData"))

```

```{r vague interval + probability}
vague_interval = 
  vague %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

vague_prob = 
  vague %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = 100*round(mean(treatPacemaker > log(1)),2))


```

```{r informative interval + probability}
# Prior info
prior_informative = rstanarm::prior_summary(informative)


prior_mean = round(exp(prior_informative$priorEvent$location), 2)
prior_ci = 
  stringr::str_c(
    round(exp(prior_informative$priorEvent$location - 
      prior_informative$priorEvent$scale * 1.96),2),
    " - ",
    round(exp(prior_informative$priorEvent$location + 
      prior_informative$priorEvent$scale * 1.96), 2)
  )


informative_interval = 
  informative %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

informative_prob = 
  informative %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = 100*round(mean(treatPacemaker > log(1)),2))

```

Bayesian approaches to survival analysis can provide a number of
benefits over the classical frequentist approach, including the ability
to make direct probability statements about parameters of interest (the
risk of pacemaker implantation), and to incorporate prior knowledge.
Using a vague prior the HR is `r vague_interval[[1]]`, 95% credible interval (CrI `r vague_interval[[2]]` - `r vague_interval[[3]]`). While the CrI
approximates the previously calculated CI, it can now be used to formulate
direct probability statements. As shown in Figure 3, the use of a
pacemaker is compatible with an `r vague_prob[[1]]`% probability of increased mortality
compared to those not receiving a pacemaker.

```{r fig3, fig.width=7, fig.height=8, include=FALSE}
# Prior info
prior_vague = rstanarm::prior_summary(vague)
SWEDEHEART_mean = broom::tidy(cox4)$estimate
SWEDEHEART_se = broom::tidy(cox4)$std.error
  
p1 = 
  vague %>%
  tidybayes::tidy_draws() %>%
  ggplot(aes(x = treatPacemaker,
             fill_ramp = stat(x > log(1)))
         ) +
  # Only posterior with  ggdist::stat_halfeye()
  ggdist::stat_halfeye(fill = "#F8D089", # distribution fill
                       # very important so all distributions are comparable
                       normalize = "none", 
                       .width = 0.95, # 95% CrI
                       point_interval = ggdist::median_hdi
                       ) +
  # To fill posterior distribution OR > 1 as gray
  ggdist::scale_fill_ramp_discrete(from = "gray85", range = c(0,1)) +
  
  # Prior 
  stat_function(fun = dnorm,
                args = c(mean = prior_vague$priorEvent$location,
                         sd = prior_vague$priorEvent$scale),
                alpha = 0.8) +
  # Original data 
  stat_function(fun = dnorm,
                args = c(mean = SWEDEHEART_mean,
                         sd = SWEDEHEART_se),
                color = "firebrick",
                linetype = 2) +
  
  # Prior
  annotate(geom = "curve",
           x = log(0.79), y = 1.4,
           xend = log(0.77), yend = 0.25, 
           curvature = .3, arrow = arrow(length = unit(1.5, "mm"))) +
  annotate(geom = "text",
           x = log(0.85), y = 1.7, label = "Vague Prior", hjust = "center") +
  
  
  # Original data
  annotate(geom = "curve",
           x = log(1.45), y = 1.76,
           xend = log(1.38), yend = 1.1, 
           curvature = .3, arrow = arrow(length = unit(1.5, "mm"))) +
  annotate(geom = "text",
           x = log(1.505), y = 1.8, label = "Data", hjust = "center") +
  
  # Posterior
  annotate(geom = "curve",
           x = log(1.28), y = 3.05,
           xend = log(1.2), yend = 2.3, 
           curvature = .3, arrow = arrow(length = unit(1.5, "mm"))) +
  annotate(geom = "text",
           x = log(1.46), y = 3.1, label = "Posterior Distribution", hjust = "center") +
  
  # Vertical line
  annotate(geom = "segment",
           x = log(1), y = 0,
           xend = log(1), yend = 2.5) +
  
  scale_y_continuous(limits = c(0, 5.7),
                     breaks = seq(0, 6, 2),
                     expand = c(0, 0.2)) +
  scale_x_continuous(breaks = log(seq(0.8, 1.7, 0.1)),
                     limits = log(c(0.75, 1.7)),
                     labels = seq(0.8, 1.7, 0.1)) +
  labs(x = "Hazard Ratio (log scale)",
       y = "Density") +
  coord_cartesian(clip = 'off') +  # Prevent cutting text at the margins
  ggdist::theme_ggdist() +
  theme(legend.position = 'none',
        plot.title.position = 'plot',
        plot.margin = margin(20, 20, 20, 20))

p2 = 
  informative %>%
  tidybayes::tidy_draws() %>%
  ggplot(aes(x = treatPacemaker,
             fill_ramp = stat(x > log(1)))
         ) +
  # Only posterior with  ggdist::stat_halfeye()
  ggdist::stat_halfeye(fill = "#E6A233", # distribution fill
                       # very important so all distributions are comparable
                       normalize = "none", 
                       .width = 0.95, # 95% CrI
                       point_interval = ggdist::median_hdi
                       ) +
  # To fill posterior distribution OR > 1 as gray
  ggdist::scale_fill_ramp_discrete(from = "gray85", range = c(0,1)) +
  
  # Prior 
  stat_function(fun = dnorm,
                args = c(mean = prior_informative$priorEvent$location,
                         sd = prior_informative$priorEvent$scale),
                alpha = 0.5) +
  # Original data 
  stat_function(fun = dnorm,
                args = c(mean = SWEDEHEART_mean,
                         sd = SWEDEHEART_se),
                color = "firebrick",
                linetype = 2) +
  
  # Prior
  annotate(geom = "curve",
           x = log(1.31), y = 3.5,
           xend = log(1.24), yend = 3.2, 
           curvature = .2, arrow = arrow(length = unit(1.5, "mm"))) +
  annotate(geom = "text",
           x = log(1.45), y = 3.5, label = "Informative Prior", hjust = "center") +
  
  
  # Original data
  annotate(geom = "curve",
           x = log(1.45), y = 1.76,
           xend = log(1.38), yend = 1.1, 
           curvature = .3, arrow = arrow(length = unit(1.5, "mm"))) +
  annotate(geom = "text",
           x = log(1.505), y = 1.8, label = "Data", hjust = "center") +
  
  # Posterior
  annotate(geom = "curve",
           x = log(1.21), y = 5.1,
           xend = log(1.15), yend = 4.7, 
           curvature = .2, arrow = arrow(length = unit(1.5, "mm"))) +
  annotate(geom = "text",
           x = log(1.37), y = 5.1, label = "Posterior Distribution", hjust = "center") +
  
  scale_y_continuous(limits = c(0, 5.7),
                     breaks = seq(0, 6, 2),
                     expand = c(0, 0.2)) +
  scale_x_continuous(breaks = log(seq(0.8, 1.7, 0.1)),
                     limits = log(c(0.75, 1.7)),
                     labels = seq(0.8, 1.7, 0.1)) +
  # Vertical line
  annotate(geom = "segment",
           x = log(1), y = 0,
           xend = log(1), yend = 1.57) +
  
  labs(x = "Hazard Ratio (log scale)",
       y = "Density") +
  coord_cartesian(clip = 'off') +  # Prevent cutting text at the margins
  ggdist::theme_ggdist() +
  theme(legend.position = 'none',
        plot.title.position = 'plot',
        plot.margin = margin(20, 20, 20, 20))

# Suppress code used to save figure
# tiff(file = here::here("output", "figures", 
#                       'fig3.tif'),
#     height=18, width=18.1, units = "cm", res = 1200)
# 
# p1 / p2 + plot_annotation(tag_levels = "A")
# 
# dev.off()
```

```{r central illustration, include=FALSE}

# Suppress code used to save figure
# tiff(file = here::here("output", "figures", 
#                       'central.tif'),
#     height=13, width=20.1, units = "cm", res = 1200)
# p2
# 
# dev.off()

```


Previously research using the same Swedish databases have examined the
risk of a pacemaker in patients undergoing SAVR [@RN5759] and found an
increased risk (HR 1.14; 95% CI, 1.01 - 1.29). Given the
similarities in the populations, everyone with aortic stenosis
undergoing treatment in the same hospitals in the same treatment
windows, it seems reasonable to use this information, down weighted as described in the Methods,  to represent our
prior beliefs. With this informative prior, the HR for the no pacemaker
group is `r prior_mean`, 95% credible interval (CrI `r prior_ci`). Given that this
informative prior is consistent with the observed TAVR data, the slight
rightward shift and narrowing of the 95% CrI of the marginal posterior
distribution compared to the marginal posterior with a vaguely informative prior
is to be expected (Figure 3). Using this informative prior, it can
be appreciated that the probability of increased mortality following a
pacemaker post TAVR is `r informative_prob[[1]]`%.

## Discussion

In this reanalysis of a recent publication from the SWEDEHEART
registry [@RN5758], we were able to reliably extract the individual
patient data concerning TAVR mortality as a function of receiving or not
a permanent cardiac pacemaker. As the original analysis used a 10-year
follow-up window and as the hazard ratios varied over time, we analyzed
the risk associated with a cardiac pacemaker using a shorter 4-year
window. This has the advantages of being a period when the hazard ratios
appear constant as well as providing results in a more clinically
pertinent risk window. Certainly, one could argue that examining relative
risks at 10 years when the mean entry age is 81 is of limited value since
most patients will be deceased by this time, independently of the
presence or absence of a pacemaker following their TAVR. Our standard
survival analysis using 4-year mortality as the outcome revealed an
increased risk following pacemaker insertion (HR = `r tidy_cox4$estimate`, 95% CI `r tidy_cox4$conf.low` -
`r tidy_cox4$conf.high`) which not reach statistical significance (p = `r tidy_cox4$p.value`). However, the
goal of this re-analysis was not to evaluate statistical significance
but rather to estimate the probability of any increase in total
mortality experienced by the pacemaker group. The estimation of this
parameter requires a formal Bayesian survival analysis.

The Bayesian analysis with a vague prior revealed an `r vague_prob[[1]]`%
probability of increased mortality among TAVR patients requiring a
pacemaker group compared those not requiring the same. The probability of
increased mortality is augmented to an `r informative_prob[[1]]`% probability when informative prior knowledge about the risk of mortality with pacemakers in
aortic stenosis patients undergoing SAVR is integrated into the decision
calculus.

By concentrating on parameter estimation rather than on
null hypothesis statistical testing and by incorporating relevant
background knowledge, this Bayesian analysis arguably leads to a more
insightful assessment of the risks of pacemakers following TAVR. Using
aggregate data from previous clinical trials, multiple publications have
demonstrated the additional advantages of Bayesian re-analyses [@brophy; @goligher]. The
current article suggests that similar benefits may be observed when
this approach is applied to individual patient data in the context of an
observational research design.

Our study also has limitations. First, actual individual data was unavailable, which did not allow us to perform adjusted analysis with relevant covariates, limiting appropriate confounding control. Yet, we note that our frequentist results using extracted data from the reported Kaplan--Meier curve were very similar to the original paper. Thus, it is unlikely that a Bayesian analysis with actual individual data would yield highly different results compared to the ones reported in the present article. Second, because we limited our analysis to data extracted from Kapla--Meier curves, we could only reanalyze the all-cause mortality outcome. Third, these analyses were not preregistered; hence, they are exploratory and should be interpreted with caution. Lastly, we limited our analyses to a restricted number of priors and did not perform thorough sensitivity analyses regarding our Bayesian analyses.

In conclusion, while the original publication concluded there was "no difference in long-term survival between
patients who did and did not undergo permanent pacemaker implantation
after TAVR", this Bayesian reanalysis suggests a moderate to high probability that pacemaker implantation is associated with increased mortality in the first 4 years following TAVR.

# Perspectives

- What Is Known?

- What Is New?

- What Is Next?

For Original Research Papers, authors should outline the following:
What Is Known? (what is the background that generates the question that is
being addressed);
What Is New? (what did this study add);
What Is Next? (what is needed to improve our knowledge base).
These should be no longer than 1 paragraph, i.e. 3–4 sentences. Authors are
asked to consider the clinical implications of their paper and identify areas of clinical relevance that could be used by clinician readers as professional caregivers. This applies not only to physicians in training, but also to the sustained commitment to education and continuous improvement across the span of their professional careers.

# References

<div id="refs"></div>

# Figure Titles and Legends

Figure 1: Reconstructed Kaplan--Meier curve

This figure shows the reconstructed Kaplan--Meier all-cause mortality curve regarding the individual-patient data extracted from the propensity score-matched cohort. 

<br>

Figure 2: Difference in Survival Probability Across Time

This figure shows the difference in survival probabilities along with 95% confidence intervals (gray area) across time in years. A difference smaller than zero indicates
lower survival probability in patients exposed to pacemaker.

<br>

```{r}

CI_prior_informative = 
  data.frame(estimate = prior_informative$priorEvent$location,
             se = prior_informative$priorEvent$scale) %>% 
  dplyr::mutate(conf.low = estimate - 1.96*se,
                conf.high = estimate + 1.96*se) %>% 
  dplyr::summarise(dplyr::across(c(estimate, conf.low, conf.high),
                                 ~round(exp(.),2)))


```


Figure 3: Data, Prior, and Posterior Distributions of the Hazard Ratio (4-year time window)

These figures show the underlying data along with Bayesian priors and marginal posterior distributions regarding analyses restricted to 4-year time-window. Interval bars depict the median and 95% credible intervals of each marginal posterior distribution. Colored filled areas depict the area under the curve above HR of 1.0, which represents the posterior probability above 1.0 (`r vague_prob[[1]]`% in Panel A, and `r informative_prob[[1]]`% in Panel B). In both panels, "Data" regards the result from the frequentist Cox proportional hazards model restricted to 4-year time-window (HR = `r tidy_cox4$estimate`, 95% CI `r tidy_cox4$conf.low` - `r tidy_cox4$conf.high`). Moreover, Panel A shows a vague, flat prior (Normal[0, 2.5] in the log scale) along with the resulting marginal posterior distribution. Panel B shows the informative prior based on previous work, yet downweighted by 50% (HR = `r CI_prior_informative$estimate`, 95% CI `r CI_prior_informative$conf.low` - `r CI_prior_informative$conf.high`) along with the resulting marginal posterior distribution. 

