---
output:
  word_document: default
bibliography: references.bib
csl: jacc.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE,
                      error=FALSE, warning=FALSE, comment=NA)

```

```{r packages}
# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

pacman::p_load(tidyverse,
               rms,
               survival,
               survminer,
               here,
               tidybayes,
               patchwork)

pacman::p_load_gh("BlakeRMills/MetBrewer")

# Download rstanarm's "Survival Analysis Version" 
# https://github.com/stan-dev/rstanarm

# install.packages("rstanarm", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

library(rstanarm)
               
theme_set(bayesplot::theme_default(base_family = "sans"))

```

**Title**:

Pacemaker Risk Following Transcatheter Aortic Valve Replacement - A Bayesian Reanalysis 

**Running Title**:

Pacemaker Risk Following TAVR

**Authors**:

Arthur M. Albuquerque1 and James M. Brophy2

1 School of Medicine, Universidade Federal do Rio de Janeiro, Brazil; This author takes responsibility for all aspects of the reliability and freedom from bias of the data presented and their discussed interpretation

2 McGill Health University Center, Montreal, Canada; This author takes responsibility for all aspects of the reliability and freedom from bias of the data presented and their discussed interpretation

**Corresponding author**:

James Brophy MD PhD       
Professor of Medicine & Epidemiology (McGill University)       
McGill University Health Center       
1001 Decarie Blvd Room C04.1410        
Montreal (Qc) H4A 3J1       
e-mail: james.brophy@mcgill.ca       

**Funding**:

JMB is a research scholar supported by Les Fonds de Recherche Québec Santé which had no influence on the choice of topic, the results, or conclusions. 

**Conflicts of Interest Disclosures**:

Both authors do not report any potential conflicts of interest.

**Word Count**: 

2599

\newpage

**Structured Abstract**: (212 words)

Objectives: To estimate the probability of increased total mortality risk in patients receiving a cardiac pacemaker following transcatheter aortic valve replacement (TAVR).

Background: A recent publication of a nationwide Swedish, population-based cohort study found no statistically significant difference for all-cause mortality. There are several reasons to query the robustness of this analysis and to investigate if a Bayesian reanalysis would lead to the same conclusion. 

Methods: A digitalized approach to the published Kaplan -- Meier curves to permit the  reconstruction of the
individual patient dataset. Bayesian survival analyses of this data using both vague, thereby  allowing the posterior probability to be completely dominated by the observed data, and informative priors, based on the mortality risk of pacemaker implantation following surgical aortic valve replacement, were performed.

Results: Individual patient data was reliably extracted and showed an increased risk at 4 year follow-up (Hazard ratio (HR) = 1.08, 95% CI 0.85 - 1.36). The Bayesian analysis using a vague prior revealed a 75% probability of increased mortality in the pacemaker group. Using an informative prior, the posterior probability of increased mortality following pacemaker insertion was increased to 94%.

Conclusions: In contrast to the original publication, this Bayesian reanalysis suggests a moderate to high probability of an increased total mortality in TAVR patients following pacemaker implantation.

**Key Words**: Pacemaker, mortality, Bayesian

\newpage

# Text

## Introduction

Recently, a nationwide Swedish, population-based cohort study found no
statistically significant difference for all-cause mortality (hazard ratio [HR] 1.03; 95% CI: 0.88 - 1.22; P = 0.692) in patients who underwent permanent pacemaker implantation after transcatheter aortic valve replacement (TAVR) between 2008 and
2018 [@RN5758]. Leading the authors to conclude that long-term survival
between patients who did and did not undergo permanent pacemaker
implantation after TAVR was not different. While the study included a
large unselected sample of 3,420 TAVR patients, there are a number of
reasons why it is of interest to query the strength of the evidence
supporting their conclusion. 

First, their central Kaplan--Meier curve shows survival curves crossing,
raising the possibility of a time-varying HR such that the proportional
hazards assumptions underlying their analysis may not be valid. Second
given this is an elderly population (mean age \> 81), the performed
comparative lifetime analysis with some patients followed up to 10
years may not be the most informative and clinically relevant. As
eventually we all die, this analysis perhaps obscures some earlier
clinically pertinent mortality differences among those receiving and not
receiving pacemakers post-TAVR. Thirdly, the same nationwide databases
have examined the mortality impact of pacemaker implantation in a
contemporary population of aortic stenosis patients undergoing surgical
aortic valve replacement (SAVR) [@RN5759] and the inclusion of all or
some of this additional evidence may be informative. 

A Bayesian analysis [@RN4985] can directly estimate the probability of
increased mortality post pacemaker insertion and allows the
incorporation of past knowledge which may be helpful in furthering our
understanding of this data and in presenting actionable probabilities.

## Methods

### Data source

To gain approximate access to this dataset, we digitalized the reported
Kaplan--Meier mortality curve in the propensity score-matched cohort [@RN5758]. We extracted this data instead of from the full cohort since propensity score matching yields more balanced comparative groups than provided by the crude data. This was operationalized by
following the technique of Guyot [@RN5762], utilizing
the website WebPlotDigitalizer and the R
programming language [@R]. Specifically, the R package IPDfromKM [@IPDfromKM] created this reconstruction of the
individual patient data thereby
allowing our secondary Bayesian survival analyses to be performed. 

### Outcome

While the original publication examined several different outcomes, this
analysis is limited to the main outcome of total mortality as that is
the only outcome for which we can estimate Kaplan--Meier-derived
individual patient data (IPD). Given that the median follow-up is 2.7
years, that the KM slopes appear to change beyond 4 years and that
assessing the impact of pacemaker implantation seems clinically most
relevant in this shorter time window, we prespecified a maximum 4 year
follow-up for our analyses.


### Statistical analyses

Bayesian approaches to survival analysis can provide a number of
benefits over the classical frequentist approach, including the ability
to make direct probability statements about parameters of interest (the
risk of pacemaker implantation), and to incorporate prior knowledge. These probability statements arise from the posterior distribution according to the following equation:     
 $$ \text{Posterior}  = \frac{\text{Probability of the data} * \text{Prior}}{\text{Normalizing Constant}} $$

Therefore, in addition to the current data summarized by the probability of the data (likelihood function) one requires a prior probability distribution each parameter. The robustness of the Bayesian approach is often assessed by sensitivity analyses that examine the variation in the posterior probability as a function of the choice of different prior distributions.  

The mechanics of the Bayesian analyses were performed using the Stan programming
language [@stan] through the R package 
rstanarm [@rstanarm] . We fitted a proportional hazard regression model using cubic M-splines for the baseline hazard. Bayesian analyses require a prior distribution for each parameter. In this model, parameters were the intercept, M-spline coefficients, and coefficient regarding the risk of pacemaker exposure. Because our focus in this article was on the latter, we used rstanarm's default vague priors for the intercept and M-spline coefficients (Normal[0, 20] and Dirichlet[1, 1, 1, ...], respectively) in all analyses.

To estimate pacemaker exposure's marginal posterior distribution (log hazard ratio between pacemaker and no pacemaker groups), we used four different priors. First we performed the analysis using rstanarm's built-in default vague prior (Normal [0, 2.50]; mean and standard deviation prior).  This prior contributes very little information to the posterior distribution and allows it to be completely dominated by the data. Second, we used an skeptical prior based on Placement of Aortic Transcatheter Valve Among (PARTNER) studies with patients at intermediate or high surgical risk who underwent TAVR [@ARNOLD]. We extracted their 1-year mortality adjusted hazard ratio on pacemaker exposure to generate this prior (Normal [-0.01, 0.21]). Third, we used an informative prior (Normal[0.13, 0.094])
based on a previous study, using the nationwide Swedish databases as the article reanalyzed here [@RN5758], but in a cohort undergoing SAVR [@RN5759]. We downweighted the influence of this informative prior by 50%, because while the populations are similar (everyone has aortic stenosis), the aortic valve interventions were different and the long term evolution of SAVR patients receiving pacemakers may not be identical to TAVR patients. To downweight, we increased the original standard error by 50% (hereafter, SAVR 50%). Lastly, we created a prior based on the same data,
but with 100% of weight (Normal[0.13, 0.062]; hereafter, SAVR 100%).

Marginal posterior distributions are summarized with medians and 95% highest-density intervals (credible intervals), defined as the narrowest interval containing 95% of the probability density function [@mcelreath2020]. We not only calculated the posterior probability of any harm
(HR >1.00), but also of greater harms (HR >1.10 and HR >1.25). In addition,
we converted hazard ratio marginal posterior distributions
to the absolute scale (risk difference [RD]) and estimated different
posterior probabilities (RD >0%, RD >1%, and RD >5%).
We assumed a baseline mortality risk (no pacemaker group) of 39.9% at 4 years
[@Skoetz], based on the digitalized extracted data mentioned above [@RN5758].

All analyses were executed within the integrated development environment
of RStudio and the statistical code can be found on
Github (https://github.com/brophyj/tavr_pace). 

## Results

### Verifying individual data extraction

```{r load 8 years data}
# load the complete digitalized KM datasets
load(here::here("output/data/both_ipd8.RData"))
```

```{r frequentist cox}
# Fit Cox
cox <- survival::coxph(survival::Surv(time, status) ~ 1 + treat,
                       data = both_ipd8)

tidy_cox = 
  broom::tidy(cox, conf.int = T, exponentiate = T) %>% 
  select(-1) %>% 
  round(2)

```

Quality assessment of our Kaplan--Meier-derived IPD data extraction was
performed analytically by comparing our extracted overall hazard ratio and 95%
CI with the published values, and graphically by checking the derived Kaplan--Meier (KM) curves (Figure
1) with the published propensity-matched KM curve (Original
Supplemental Figure 2[@RN5758]). Not only is the data extraction judged to be
adequate graphically but also numerically with a calculated HR = `r tidy_cox$estimate`,
95% CI `r tidy_cox$conf.low` - `r tidy_cox$conf.high` which compares favorably with the published value (HR: 0.99; 95% CI: 0.81 - 1.21).


```{r fig1, fig.height=5, fig.width=5.5, include=FALSE}

fig1 <- survminer::ggsurvplot(
    fit = survival::survfit(survival::Surv(time, status) ~ 1 + treat,
                            data = both_ipd8), 
    censor = F,
    xlab = "Time (years)", 
    ylab = "Cumulative Survival",
    conf.int = FALSE,
    xlim = c(0,8),
    ylim = c(0, 1),
    color = "strata",
    palette = c("black", "#EA3324"),
    risk.table = TRUE,
    risk.table.col = "strata", # Risk table color by groups
    legend.labs = c("No pacemaker", "Pacemaker"),    # Change legend labels
    risk.table.height = 0.3,
    legend.title = " ") 

# Suppress code used to save figure

# tiff(file = here::here("submissions", "IJC", "01_revision",
#                        'fig1.tif'),
#    height=14, width=18.1, units = "cm", res = 300)
 
print(fig1, newpage = FALSE)
 
# dev.off()

```

```{r diagnostics cox}

cox.zph <- survival::cox.zph(cox)  

# survminer::ggcoxzph(cox.zph)
# survminer::ggcoxdiagnostics(cox, type = "deviance", linear.predictions = FALSE)
```


The difference in survival probabilities with the 95% CI is plotted in
Figure 2. One of the concerns with the original analysis was the
possibility of time-varying proportional hazards which are again
suggested in this Figure. However, statistical tests suggested the
proportional hazards assumption was not violated (p = `r round(cox.zph$table[1,3],2)`), although it
bears mentioning that the power to detect violations with this sample
size is limited [@Austin].

```{r fig2 output, fig.width=5.5, fig.height=4, include=FALSE}
f <- rms::npsurv(survival::Surv(time, status) ~ 1 + treat,
                            data = both_ipd8)


# Suppress code used to save figure

# tiff(file = here::here("submissions", "IJC", "01_revision",
#                       'fig2.tif'),
#     height=14, width=20.1, units = "cm", res = 300)
# 
# par(mar= c(4.2,6,2,3)) 

fig2 <- rms::survdiffplot(f,
                          order=2:1, # "Pacemaker" minus "No pacemaker"
                          time.inc=1,
                          conf.int = 0.95,
                          conf="shaded",
                          xlab = "Time (years)")
# dev.off()
```

### Standard survival analysis to 4 years

```{r load 4 years data}
# load the 4-years digitalized KM datasets
load(here::here("output/data/both_ipd4.RData"))
```

```{r cox 4 years}

# Fit Cox for 4 year data
cox4 <- survival::coxph(survival::Surv(time, status) ~ 1 + treat,
                       data = both_ipd4)

tidy_cox4 = 
  broom::tidy(cox4, conf.int = T, exponentiate = T) %>% 
  select(-1) %>% 
  round(2)

```

Even if the proportional hazards assumptions are not violated,
clinically it is indicated to investigate the risks over a more
restricted time window. In accordance also with the varying risks, we
elected a priori to concentrate on a 4-year time window. Using this time
frame, we extracted the individual data as described in the Methods section
above. The frequentist Cox proportional hazards model analysis for this
more restricted data set results in a HR = `r tidy_cox4$estimate`, 95% CI `r tidy_cox4$conf.low` - `r tidy_cox4$conf.high`, p =
`r tidy_cox4$p.value`. While this remains statistically not significant, the point
estimate has clearly moved towards an increased mortality risk in the 
pacemaker group. Using this statistically non-sgnificant result to conclude that a pacemaker does
not influence 4-year mortality risks makes the common error of confusing absence of
evidence with evidence of absence. To avoid the nullism and dichotomania associated with null hypothesis significance testing[@RN5433], we next explored the data with a Bayesian survival analysis. 

### Bayesian survival analysis

```{r load bayesian models}

# Posteriors
load(here::here("output/fit/bayesian_model_vague.RData"))
load(here::here("output/fit/bayesian_model_skeptical.RData"))
load(here::here("output/fit/bayesian_model_informative.RData"))
load(here::here("output/fit/bayesian_model_informative_100.RData"))

```

```{r vague interval + probability}
vague_interval = 
  vague %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

vague_prob = 
  vague %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))


```


Bayesian approaches to survival analysis can provide a number of
benefits over the classical frequentist approach, including the ability
to make direct probability statements about parameters of interest (the
risk of pacemaker implantation), and to incorporate prior knowledge.
Using a vague prior the HR at a 4 year time point is `r vague_interval[[1]]`,
95% credible interval (95% CrI `r vague_interval[[2]]` - `r vague_interval[[3]]`).
While the CrI approximates the previously calculated CI, it can now be used to
formulate direct probability statements. As shown in Figure 3 and Table 1, the
use of a pacemaker is compatible with an `r vague_prob[[1]]`% probability of
increased mortality compared to those not receiving a pacemaker. 

```{r skeptical interval + probability}
skeptical_interval = 
  skeptical_model %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

skeptical_prob = 
  skeptical_model %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))


```

While the incorporation of a vague prior allows one to calculate posterior
probabilities, it does not introduce relevant external information into the
analysis, limiting the extent to which the Bayesian framework can contribute.
Further analyses with more informative
priors could cover different beliefs on this subject. When assuming a skeptical
prior based on a large observational study [@ARNOLD], there is a apparent power
increase, represented by the narrower credible interval
(95% CrI `r skeptical_interval[[2]]` - `r skeptical_interval[[3]]`), and smaller
probability of increased mortality (Figure 3 and Table 1).

```{r SAVR 50% interval + probability}
informative_interval = 
  informative %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

informative_prob = 
  informative %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))

```

```{r SAVR 100% interval + probability}
informative100_interval = 
  informative_100 %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

informative100_prob = 
  informative_100 %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))


```

To further comprise other beliefs, we also reanalyzed this data using priors
based on the same Swedish databases, but in patients undergoing SAVR [@RN5759].
The choice for this belief was based on the similarities in the populations,
everyone with aortic stenosis undergoing treatment in the same hospitals in the
same treatment windows. With this informative prior downweighted by 50%
(SAVR 50%), there is shift towards greater mortality association with pacemaker
exposure (HR `r informative_interval[[1]]`, 95% CrI
`r informative_interval[[2]]` - `r informative_interval[[3]]`), along with
greater probability of HR > 1 (`r informative_prob[[1]]`%, Table 1). Without
any downweight on the prior (SAVR 100%), the marginal posterior distribution
shifts further from HR of 1 (Figure 3 and Table 1). 

Another advantage of Bayesian analyses is the ability to calculate posterior
probabilities other than of any harm (HR > 1), such as of 10% harm increase
(HR > 1.10) or 25% increase (HR > 1.25). These posterior probabilities are shown
for all beliefs in Table 1.

Lastly, to aid clinical decision-making, we estimated the marginal
posterior distributions on risk differences (RDs). These distributions varied
according to the underlying belief (Supplementary Table 1). The posterior probabilities 
of any harm on both relative (HR > 1.00, Table 1) and absolute scale (RD > 0%, 
Supplementary Table 1) are, as expected, identical. Moreover, we estimated
the posterior probabilities of absolute mortality increase association with 
pacemaker exposure by 1% and 5%. The posterior probability of RD > 1% varied
between 58.0% to 94%.


## Discussion

In this reanalysis of the recent SWEDEHEART
registry  publication[@RN5758], we were able to reliably extract the individual
patient data concerning TAVR mortality as a function of receiving or not
a permanent cardiac pacemaker. The original analysis used a 10-year
follow-up window and as the hazard ratios varied over time, we analyzed
the risk associated with a cardiac pacemaker using a shorter 4-year
window. This has the advantages of being a period when the hazard ratios
appear constant as well as providing results in a more clinically
pertinent risk window. Certainly, one could argue that examining relative
risks at 10 years when the mean entry age is 81 is of limited value since
most patients will be deceased by this time, independently of the
presence or absence of a pacemaker following their TAVR. Our standard
survival analysis using 4-year mortality as the outcome revealed an
increased risk following pacemaker insertion (HR = `r tidy_cox4$estimate`, 95% CI `r tidy_cox4$conf.low` -
`r tidy_cox4$conf.high`) which not reach statistical significance (p = `r tidy_cox4$p.value`). However, the
goal of this re-analysis was not to evaluate statistical significance
but rather to estimate the probability of any increase in total
mortality experienced by the pacemaker group. The estimation of this
parameter requires a formal Bayesian survival analysis.

The Bayesian analysis with a vague prior revealed an `r vague_prob[[1]]`%
probability of increased mortality among TAVR patients requiring a
pacemaker group compared those not requiring the same. The probability of
increased mortality is augmented to an `r informative_prob[[1]]`% probability when informative prior knowledge about the risk of mortality with pacemakers in
aortic stenosis patients undergoing SAVR is integrated into the decision
calculus.

By concentrating on parameter estimation rather than on
null hypothesis statistical testing and by incorporating relevant
background knowledge, this Bayesian analysis arguably leads to a more
insightful assessment of the risks of pacemakers following TAVR. Using
aggregate data from previous clinical trials, multiple publications have
demonstrated the additional advantages of Bayesian re-analyses [@brophy; @goligher]. The
current article suggests that similar benefits may be observed when
this approach is applied to individual patient data in the context of an
observational research design.

Our study also has limitations. First, actual individual data was unavailable, which did not allow us to perform adjusted analysis with relevant covariates, limiting appropriate confounding control. Yet, we note that our frequentist results using extracted data from the reported Kaplan--Meier curve were very similar to the original paper. Thus, it is unlikely that a Bayesian analysis with actual individual data would yield highly different results compared to the ones reported in the present article. Second, because we limited our analysis to data extracted from Kaplan--Meier curves, we could only reanalyze the all-cause mortality outcome. Third, these analyses were not preregistered; hence, they are exploratory and should be interpreted with caution. Lastly, we limited our analyses to a restricted number of priors and did not perform an extensive sensitivity analyses regarding our Bayesian analyses.

In conclusion, while the original publication concluded there was "no difference in long-term survival between
patients who did and did not undergo permanent pacemaker implantation
after TAVR", this Bayesian reanalysis suggests a moderate to high probability that pacemaker implantation is associated with increased mortality in the first 4 years following TAVR.
<br>
<br>
<br>

\newpage

# References

<div id="refs"></div>

\newpage

# Table 1

<br><br>

```{r table1}
hr_table_fun = function(model, col_name){
  HR = 
    model |> 
    tidybayes::tidy_draws() |> 
    dplyr::summarise(HR = exp(treatPacemaker))
  
  colnames(HR) = col_name
  
  return(HR)
}

HRs = hr_table_fun(vague, "Vague") |> 
  dplyr::bind_cols(
    hr_table_fun(skeptical_model, "Skeptical"),
    hr_table_fun(informative, "SAVR 50%"),
    hr_table_fun(informative_100, "SAVR 100%"),
  ) |> 
  tidyr::pivot_longer(1:4)

HRcri95 = 
  HRs |> 
  dplyr::group_by(name) |> 
  ggdist::median_hdi(value) |> 
  dplyr::mutate(dplyr::across(value:.upper, ~round(.,2))) |> 
  dplyr::summarise("Belief" = name,
                   "HR (95% CrI)" = stringr::str_c(
                     value, " (", .lower, ", ", .upper, ")"))

HRsprobs = 
  HRs |> 
  dplyr::group_by(name) |> 
  dplyr::summarise("HR >1.00" = mean(value > 1),
                   "HR >1.10" = mean(value > 1.1),
                   "HR >1.25" = mean(value > 1.25)) |> 
  dplyr::mutate(dplyr::across(2:4, ~round(100*.,1))) |> 
  dplyr::rename("Belief" = name)

dplyr::left_join(HRcri95, HRsprobs) |> 
  dplyr::mutate(Belief = forcats::fct_rev(Belief)) |> 
  dplyr::arrange(Belief) |> 
  flextable::flextable() |> 
  flextable::autofit() |> 
  flextable::add_header_row(top = TRUE, 
                            values = c(" ", "Posterior probability, %"), 
                            colwidths = c(2, 3)) |> 
  flextable::theme_box() |> 
  flextable::add_footer_lines('"SAVR 50%" regards posterior distribution while assuming a prior based on the surgical aortic valve replacement SWEDEHEART data with 50% of weight. "SAVR 100%" regards the same data, but with 100% weight.') |> 
  flextable::add_footer_lines('Abbreviation: HR, hazard ratio')
```

\newpage

# Figure Titles and Legends

Figure 1: Reconstructed Kaplan--Meier curve

This figure shows the reconstructed Kaplan--Meier all-cause mortality curve regarding the individual-patient data extracted from the propensity score-matched cohort. 

<br>

Figure 2: Difference in Survival Probability Across Time

This figure shows the difference in survival probabilities along with 95% confidence intervals (gray area) across time in years. A difference smaller than zero indicates
lower survival probability in patients exposed to pacemaker.

<br>

Figure 3: Prior and Posterior Distributions of the Hazard Ratio (4-year time window)

Underlying prior and marginal posterior distributions regarding analyses restricted to 4-year time-window (Table 1). Panel A, Vague belief; B, Skeptical; C, SAVR 50%; D, SAVR 100%. Dashed lines depict the underlying prior distributions. Color filled distributions represent the marginal posteriors. Interval bars depict the median and 95% credible intervals of each marginal posterior distribution. Colored filled areas depict the area under the curve above HR of 1.0, which represents the posterior probability above 1.0. These probabilities are also shown in each panel. 

```{r fig3 helper function}
prior_vague = rstanarm::prior_summary(vague)
prior_skeptical = rstanarm::prior_summary(skeptical_model)
prior_informative50 = rstanarm::prior_summary(informative)
prior_informative100 = rstanarm::prior_summary(informative_100)

plot_fun = function(model, pp, y_end, color, xlab = F, ylab = F) {
  model |> 
  tidybayes::tidy_draws() |> 
  ggplot(aes(x = treatPacemaker,
             fill = stat(x > log(1)),
             slab_alpha = stat((x)))
         ) +
  # Only posterior with  ggdist::stat_halfeye()
  ggdist::stat_halfeye(# very important so all distributions are comparable
                       normalize = "none", 
                       fill_type = "gradient",
                       .width = 0.95, # 95% CrI
                       point_interval = ggdist::median_hdi
                       ) +
 # scale_slab_alpha_continuous(range = c(-0.2, 1.25)) +
  scale_fill_manual(values = c("gray80", color)) +
  
  # Prior 
  stat_function(fun = dnorm,
                args = c(mean = pp$priorEvent$location,
                         sd = pp$priorEvent$scale),
                alpha = 0.8,
                linetype = 2) +
  
  # Vertical line
  annotate(geom = "segment",
           x = log(1), y = 0,
           xend = log(1), yend = y_end) +
  
  scale_y_continuous(limits = c(0, 7),
                     breaks = seq(0, 6, 2),
                     expand = c(0, 0.4)) +
  scale_x_continuous(breaks = log(seq(0.8, 1.5, 0.1)),
                     limits = log(c(0.75, 1.55)),
                     labels = seq(0.8, 1.5, 0.1)) +
  labs(x = NULL,
       y = " ") +
  {if (xlab) labs(x = "Hazard Ratio (log scale)")} +   
  {if (ylab) labs(y = "Density")} + 
  ggdist::theme_ggdist() +
  theme(legend.position = 'none',
        plot.title.position = 'plot',
        plot.margin = margin(20, 20, 20, 20))
  
}
```

```{r fig3, include = FALSE}
pal = MetBrewer::met.brewer(name="Isfahan1",n=7,type="discrete")

p1 = plot_fun(vague, prior_vague,
              y_end = 2.5, color = pal[3],
              ylab = T) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[4, "HR >1.00"], "%"))


p2 = plot_fun(skeptical_model, prior_skeptical,
              y_end = 3.05, color = pal[2]) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[3, "HR >1.00"], "%"))

p3 = plot_fun(informative, prior_informative50,
              y_end = 1.5, color = pal[4],
              xlab = T, ylab = T) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[2, "HR >1.00"], "%"))

p4 = plot_fun(informative_100, prior_informative100,
              y_end = 0.65, color = pal[6],
              xlab = T) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[1, "HR >1.00"], "%"))

# Suppress code used to save figure
# tiff(file = here::here("submissions", "IJC", "01_revision",
#                       'fig3.tif'),
#     type = "cairo", # to show the gradient from ggdist
#     height=12, width=20, units = "cm", res = 300)

p1 + p2 + p3 + p4 + patchwork::plot_annotation(tag_levels = "A")

# dev.off()
```

