---
output:
  word_document: default
bibliography: references.bib
csl: jacc.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE,
                      error=FALSE, warning=FALSE, comment=NA)

```

```{r packages}
# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

pacman::p_load(tidyverse,
               rms,
               survival,
               survminer,
               here,
               tidybayes,
               patchwork)

pacman::p_load_gh("BlakeRMills/MetBrewer")

# Download rstanarm's "Survival Analysis Version" 
# https://github.com/stan-dev/rstanarm

# install.packages("rstanarm", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

library(rstanarm)
               
theme_set(bayesplot::theme_default(base_family = "sans"))

```

**Title**:

Pacemaker Risk Following Transcatheter Aortic Valve Replacement - A Bayesian Reanalysis 

**Running Title**:

Pacemaker Risk Following TAVR

**Authors**:

Arthur M. Albuquerque1 and James M. Brophy2

1 School of Medicine, Universidade Federal do Rio de Janeiro, Brazil; This author takes responsibility for all aspects of the reliability and freedom from bias of the data presented and their discussed interpretation

2 McGill Health University Center, Montreal, Canada; This author takes responsibility for all aspects of the reliability and freedom from bias of the data presented and their discussed interpretation

**Corresponding author**:

James Brophy MD PhD       
Professor of Medicine & Epidemiology (McGill University)       
McGill University Health Center       
1001 Decarie Blvd Room C04.1410        
Montreal (Qc) H4A 3J1       
e-mail: james.brophy@mcgill.ca       

**Funding**:

JMB is a research scholar supported by Les Fonds de Recherche Québec Santé which had no influence on the choice of topic, the results, or conclusions. 

**Conflicts of Interest Disclosures**:

Both authors do not report any potential conflicts of interest.

**Word Count**: 

2481

\newpage

**Structured Abstract**: (212 words)

Objectives: To estimate the probability of increased total mortality risk in
patients receiving a cardiac pacemaker following transcatheter aortic valve
replacement (TAVR).

Background: A recent publication of a nationwide Swedish, population-based
cohort study found no statistically significant difference for all-cause
mortality. It is unknown if a Bayesian reanalysis would provide additional
insights and lead to the same conclusion.

Methods: A digitalized approach to the published Kaplan – Meier curves was used
to reconstruct the individual patient dataset. Bayesian survival analyses of
this data using both vague, thereby allowing the posterior probability to be
completely dominated by the observed data, as well as skeptical and informative
priors, based on the mortality risk of pacemaker implantation following surgical
aortic valve replacement, were performed.

Results: The individual patient data set was reliably reconstructed and showed
a 4 year follow-up hazard ratio (HR) = 1.08, 95% credible interval (CrI) 0.85
- 1.36. The Bayesian analysis using a vague prior revealed a 74.9% probability
of increased mortality in the pacemaker group. Using a skeptical,
semi-informative, and fully informative priors, the posterior probabilities of
increased mortality following pacemaker insertion was increased to 68.9%, 93.9%
and 98.4%, respectively.

Conclusions: This Bayesian reanalysis suggests a moderate to high probability of
an increased total mortality in TAVR patients requiring post procedural
pacemaker implantation.


**Key Words**: Pacemaker, mortality, Bayesian

\newpage

# Text

## Introduction

Recently, a nationwide Swedish, population-based cohort study found no
statistically significant difference for all-cause mortality (hazard ratio
[HR] 1.03; 95% CI: 0.88 - 1.22; P = 0.692) in patients who underwent permanent
pacemaker implantation after transcatheter aortic valve replacement (TAVR)
between 2008 and 2018 [@RN5758]. While the study included a large unselected sample
of 3,420 TAVR patients, there are a number of reasons why it is of interest to
query the strength of the evidence supporting the conclusion that long-term
survival between patients who did and did not undergo permanent pacemaker
implantation after TAVR is not different.

First, their central Kaplan--Meier curve shows survival curves crossing,
raising the possibility of a time-varying HR such that the proportional
hazards assumptions underlying their analysis may not be valid. Second
given this is an elderly population (mean age \> 81), the performed
comparative lifetime analysis with some patients followed up to 10
years may not be the most informative and clinically relevant. As
eventually we all die, this analysis perhaps obscures some earlier
clinically pertinent mortality differences among those receiving and not
receiving pacemakers peri-TAVR. Thirdly, the same nationwide databases
have examined the mortality impact of pacemaker implantation in a
contemporary population of aortic stenosis patients undergoing surgical
aortic valve replacement (SAVR) [@RN5759] and the inclusion of all or
some of this additional evidence may be informative. 

A Bayesian analysis [@RN4985] can directly estimate the probability of
increased mortality post pacemaker insertion and allows the
incorporation of past knowledge which may be helpful in furthering our
understanding of this data and in presenting actionable probabilities.

## Methods

### Data source

To gain approximate access to this dataset, we digitalized the reported
Kaplan--Meier mortality curve in the propensity score-matched cohort [@RN5758]. We extracted this data instead of from the full cohort since propensity score matching yields more balanced comparative groups than provided by the crude data. This was operationalized by
following the technique of Guyot [@RN5762], utilizing
the website WebPlotDigitalizer and the R
programming language [@R]. Specifically, the R package IPDfromKM [@IPDfromKM] created this reconstruction of the
individual patient data thereby
allowing our secondary Bayesian survival analyses to be performed. 

### Outcome

While the original publication examined several different outcomes, this
analysis is limited to the main outcome of total mortality as that is
the only outcome for which we can estimate Kaplan--Meier-derived
individual patient data (IPD). Given that the median follow-up is 2.7
years, that the KM slopes appear to change beyond 4 years and that
assessing the impact of pacemaker implantation seems clinically most
relevant in this shorter time window, we prespecified a maximum 4 year
follow-up for our analyses.


### Statistical analyses

Bayesian approaches to survival analysis can provide a number of benefits over
the classical frequentist approach, including the ability to make direct
probability statements about parameters of interest (the risk of pacemaker
implantation), and to incorporate prior knowledge. These probability statements
arise from the posterior distribution according to the following equation:
 $$ \text{Posterior}  = \frac{\text{Probability of the data} * \text{Prior}}{\text{Normalizing Constant}} $$

Therefore, in addition to the current data summarized by the probability of the
data (likelihood function) one requires a prior probability distribution each
parameter. The robustness of the Bayesian approach is often assessed by
sensitivity analyses that examine the variation in the posterior probability as
a function of the choice of different prior distributions.  

The mechanics of the Bayesian analyses were performed using the Stan programming
language [@stan] through the R package rstanarm [@rstanarm]. We fitted a proportional
hazard regression model using cubic M-splines for the baseline hazard. Bayesian
analyses require a prior distribution for each parameter. In this model,
parameters were the intercept, M-spline coefficients, and the pacemaker exposure
risk. Because our focus in this article was on the latter, we used rstanarm’s
default vague priors for the intercept and M-spline coefficients
(Normal[0, 20] and Dirichlet[1, 1, 1, …], respectively) in all analyses.

To assess robustness of results, we estimated pacemaker exposure’s marginal
posterior distribution (log hazard ratio between pacemaker and no pacemaker
groups) with four different priors. First we performed the analysis using
rstanarm’s built-in default vague prior (Normal [0, 2.50]; mean and standard
deviation prior). This prior contributes very little information to the
posterior distribution and allows it to be completely dominated by the data.
Second, we used a skeptical prior, defined as a low prior belief that
peri-procedural pacemaker implantation is associated with increased mortality.
This prior was based on data from the Placement of Aortic Transcatheter Valve
Among (PARTNER) 2 studies of 3,763 intermediate or high surgical risk patients
undergoing TAVR [@ARNOLD]. The reported 1-year mortality adjusted hazard ratio
for pacemaker exposure (HR 0.99; 95% CI0.65 to 1.49) was transformed to a Normal
[-0.01, 0.21] skeptical prior. Third, we used a semi - informative prior based
on a previous study, using the same nationwide Swedish databases as the article
reanalyzed here [@RN5759], but in a cohort of almost 25,000 patents undergoing
SAVR (2). This study reported an increased mortality risk with pacemaker
implantation (HR 1.14; 95%CI, 1.01-1.29) which was transformed to a
Normal[0.13, 0.094] semi - informative prior. We downweighted the influence of
this informative prior by 50%, because while the populations are similar
(everyone has aortic stenosis) and studied in the same institutions, the aortic
valve interventions were different and the long term evolution of SAVR patients
receiving pacemakers may not be identical to TAVR patients. To downweight, we
increased the original standard error by 50% (hereafter labelled “SAVR 50%”).
Lastly, we created a fully informed prior based on the same data, but with 100%
of weight (Normal[0.13, 0.062]; hereafter labelled “SAVR 100%”).

Marginal posterior distributions are summarized with medians and 95%
highest-density intervals (credible intervals), defined as the narrowest
interval containing 95% of the probability density function [@mcelreath2020].
We not only calculated the posterior probability of any harm (HR >1.00), but
also of greater harms (HR >1.10 and HR >1.25). In addition, we converted
hazard ratio marginal posterior distributions to the absolute scale (risk
difference [RD]) and estimated different posterior probabilities (RD >0%, 
RD >1%, and RD >2%). We assumed a baseline mortality risk (no pacemaker group)
of 39.9% at 4 years [@Skoetz], based on the digitalized extracted data
mentioned above [@RN5758].

All analyses were executed within the integrated development environment
of RStudio and the statistical code can be found on
Github (https://github.com/brophyj/tavr_pace). 

## Results

### Verifying individual data extraction

```{r load 8 years data}
# load the complete digitalized KM datasets
load(here::here("output/data/both_ipd8.RData"))
```

```{r frequentist cox}
# Fit Cox
cox <- survival::coxph(survival::Surv(time, status) ~ 1 + treat,
                       data = both_ipd8)

tidy_cox = 
  broom::tidy(cox, conf.int = T, exponentiate = T) %>% 
  select(-1) %>% 
  round(2)

```

Quality assessment of our Kaplan--Meier-derived IPD data extraction was
performed analytically by comparing our extracted overall hazard ratio and 95%
CI with the published values, and graphically by checking the derived Kaplan--Meier (KM) curves (Figure
1) with the published propensity-matched KM curve (Original
Supplemental Figure 2[@RN5758]). Not only is the data extraction judged to be
adequate graphically but also numerically with a calculated HR = `r tidy_cox$estimate`,
95% CI `r tidy_cox$conf.low` - `r tidy_cox$conf.high` which compares favorably with the published value (HR: 0.99; 95% CI: 0.81 - 1.21).


```{r fig1, fig.height=5, fig.width=5.5, include=FALSE}

fig1 <- survminer::ggsurvplot(
    fit = survival::survfit(survival::Surv(time, status) ~ 1 + treat,
                            data = both_ipd8), 
    censor = F,
    xlab = "Time (years)", 
    ylab = "Cumulative Survival",
    conf.int = FALSE,
    xlim = c(0,8),
    ylim = c(0, 1),
    color = "strata",
    palette = c("black", "#EA3324"),
    risk.table = TRUE,
    risk.table.col = "strata", # Risk table color by groups
    legend.labs = c("No pacemaker", "Pacemaker"),    # Change legend labels
    risk.table.height = 0.3,
    legend.title = " ") 

# Suppress code used to save figure

# tiff(file = here::here("submissions", "IJC", "01_revision",
#                        'fig1.tif'),
#    height=14, width=18.1, units = "cm", res = 300)
 
print(fig1, newpage = FALSE)
 
# dev.off()

```

```{r diagnostics cox}

cox.zph <- survival::cox.zph(cox)  

# survminer::ggcoxzph(cox.zph)
# survminer::ggcoxdiagnostics(cox, type = "deviance", linear.predictions = FALSE)
```


The difference in survival probabilities with the 95% CI is plotted in
Figure 2. One of the concerns with the original analysis was the
possibility of time-varying proportional hazards which are again
suggested in this Figure. However, statistical tests suggested the
proportional hazards assumption was not violated (p = `r round(cox.zph$table[1,3],2)`), although it
bears mentioning that the power to detect violations with this sample
size is limited [@Austin].

```{r fig2 output, fig.width=5.5, fig.height=4, include=FALSE}
f <- rms::npsurv(survival::Surv(time, status) ~ 1 + treat,
                            data = both_ipd8)


# Suppress code used to save figure

# tiff(file = here::here("submissions", "IJC", "01_revision",
#                       'fig2.tif'),
#     height=14, width=20.1, units = "cm", res = 300)
# 
# par(mar= c(4.2,6,2,3)) 

fig2 <- rms::survdiffplot(f,
                          order=2:1, # "Pacemaker" minus "No pacemaker"
                          time.inc=1,
                          conf.int = 0.95,
                          conf="shaded",
                          xlab = "Time (years)")
# dev.off()
```

### Standard survival analysis to 4 years

```{r load 4 years data}
# load the 4-years digitalized KM datasets
load(here::here("output/data/both_ipd4.RData"))
```

```{r cox 4 years}

# Fit Cox for 4 year data
cox4 <- survival::coxph(survival::Surv(time, status) ~ 1 + treat,
                       data = both_ipd4)

tidy_cox4 = 
  broom::tidy(cox4, conf.int = T, exponentiate = T) %>% 
  select(-1) %>% 
  round(2)

```

Even if the proportional hazards assumptions are not violated, clinically it is
indicated to investigate the risks over a more restricted time window. In
accordance also with the varying risks, we elected a priori to concentrate on
a 4-year time window. Using this time frame, we extracted the individual data as
described in the Methods section above. The frequentist Cox proportional hazards
model analysis for this more restricted data set results in a HR =
`r tidy_cox4$estimate`, 95% CI `r tidy_cox4$conf.low` - `r tidy_cox4$conf.high`,
p = `r tidy_cox4$p.value`. The 4 year point estimate has moved towards an
increased mortality risk in the pacemaker group, but the result remains not
statistically significant. However, using this statistically non-significant
result to conclude that a pacemaker does not influence 4-year mortality risks
makes the common error of confusing absence of evidence with evidence of
absence. To avoid the nullism and dichotomania associated with null hypothesis
significance testing[@RN5433], we next explored the data with a Bayesian
survival analysis.

### Bayesian survival analysis

```{r load bayesian models}

# Posteriors
load(here::here("output/fit/bayesian_model_vague.RData"))
load(here::here("output/fit/bayesian_model_skeptical.RData"))
load(here::here("output/fit/bayesian_model_informative.RData"))
load(here::here("output/fit/bayesian_model_informative_100.RData"))

```

```{r vague interval + probability}
vague_interval = 
  vague %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

vague_prob = 
  vague %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))


```


Using a vague prior the Bayesian HR at a 4 year time point is
`r vague_interval[[1]]`, 95% credible interval (95% CrI `r vague_interval[[2]]`
- `r vague_interval[[3]]`). While the CrI approximates the previously calculated
CI, it can now be used to formulate direct probability statements. As shown in
Figure 3 and Table 1, the use of a pacemaker is compatible with an
`r vague_prob[[1]]`% probability of increased mortality compared to those not
receiving a pacemaker, calculated as the area under the curve to the right of HR
= 1.0.

```{r skeptical interval + probability}
skeptical_interval = 
  skeptical_model %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

skeptical_prob = 
  skeptical_model %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))


```

While the incorporation of a vague prior allows one to calculate posterior
probabilities, it does not introduce relevant external information into the
analysis, limiting the extent to which the Bayesian framework can contribute.
Further analyses with more informative
priors could cover different beliefs on this subject. When assuming a skeptical
prior based on a large observational study [@ARNOLD], there is an apparent power
increase, represented by the narrower credible interval
(95% CrI `r skeptical_interval[[2]]` - `r skeptical_interval[[3]]`), and slightly
smaller probability of increased mortality (Figure 3 and Table 1).

```{r SAVR 50% interval + probability}
informative_interval = 
  informative %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

informative_prob = 
  informative %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))

```

```{r SAVR 100% interval + probability}
informative100_interval = 
  informative_100 %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::median_hdi(treatPacemaker) %>% 
  dplyr::select(1:3) %>% 
  exp() %>% 
  round(2)

informative100_prob = 
  informative_100 %>% 
  tidybayes::tidy_draws() %>% 
  summarise(prob = round(100*mean(treatPacemaker > log(1)),1))


```

Other scientifically justified beliefs can be incorporated and the robustness of
the final (posterior) probabilities assessed. For example, informative priors
based on the risk of pacemaker implantation in aortic stenosis patients from the
same Swedish databases, but undergoing SAVR [@RN5759] could be used. The choice for
this informative prior is justified by the similarities in the populations with
treatments taking place in the same hospital centers at contemporary time
windows. This informative prior may be downweighted, if so desired to account
for the additional uncertainty associated with the varying type of aortic valve
intervention. As shown in Figure 3 and Table 1, these informative priors lead to
high posterior probabilities, from `r informative_prob[[1]]`% to 
`r informative100_prob[[1]]`%, of increased 4 year mortality
following TAVR pacemaker insertion. 

Another advantage of Bayesian analyses is the ability to calculate posterior
probabilities other than of any harm (HR > 1). As shown in Table 1, while it is
somewhat unlikely that the relative risk associated with a pacemaker exceeds
a 25% increase, there is a moderate probability (34-67%) that the relative risk
exceeds a 10% increase.

such as of 10% harm increase
(HR > 1.10) or 25% increase (HR > 1.25). These posterior probabilities are shown
for all beliefs in Table 1.

Lastly, to aid clinical decision-making, we estimated the marginal
posterior distributions on risk differences (RDs). These distributions varied
according to the underlying belief (Table 1). The posterior probabilities 
of any harm on both relative (HR > 1.00, Table 1) and absolute scale (RD > 0%, 
Table 1) are, as expected, identical. Moreover, we estimated
the posterior probabilities of absolute mortality increase association with 
pacemaker exposure by 1% and 2%. The posterior probability of RD > 1% varied
between 58.0% to 94%.


## Discussion

Bayesian approaches to survival analysis can provide a number of benefits over
the classical frequentist approach, including the ability to make direct
probability statements about parameters of interest (the risk of pacemaker
implantation), and to incorporate prior knowledge. In this Bayesian reanalysis
of the recent SWEDEHEART registry publication [@RN5758], after reliably
extracting the individual patient data, we demonstrated, in contrast to the
original publication [@RN5758], a moderately high probability of increased
mortality at 4 years among TAVR recipients who received a permanent pacemaker.
The clinical importance is emphasized by acknowledging that the posterior
probability.

This reanalysis should not be seen as a criticism of the original analysis but
rather as a complimentary addition to its pertinent research question, rigorous
design and data collection. The original analysis used a 10-year follow-up
window and as the hazard ratios varied over time, we analyzed the risk
associated with a cardiac pacemaker using a shorter 4-year window. This has the
advantages of being a period when the hazard ratios appear constant as well as
providing results in a more clinically pertinent risk window. Certainly, one
could argue that examining relative risks at 10 years when the mean entry age
is 81 is of limited value since most patients will be deceased by this time,
independently of the presence or absence of a pacemaker following their TAVR.
Our standard survival analysis using 4-year mortality as the outcome revealed an
increased risk following pacemaker insertion (HR = `r tidy_cox4$estimate`, 95%
CI `r tidy_cox4$conf.low` - `r tidy_cox4$conf.high`) which not reach statistical
significance (p = `r tidy_cox4$p.value`). However, the goal of this re-analysis
was not to evaluate statistical significance but rather to estimate the
probability of any increase in total mortality experienced by the pacemaker
group. The estimation of this parameter requires a formal Bayesian survival
analysis.

The Bayesian analysis with a vague prior revealed an `r vague_prob[[1]]`%
probability of increased mortality among TAVR patients requiring a pacemaker
group compared those not requiring the same. The probability of increased
mortality is augmented to `r informative_prob[[1]]` -
`r informative100_prob[[1]]`% probability when informative prior knowledge about
the risk of mortality with pacemakers in aortic stenosis patients undergoing
SAVR is integrated into the decision calculus. This result was relatively robust
as even a skeptical prior still resulted in a 70% probability of increased
mortality following pacemaker insertion.

By concentrating on parameter estimation rather than on null hypothesis
statistical testing and by incorporating relevant background knowledge, this
Bayesian analysis arguably leads to a more insightful assessment of the risks of
pacemakers following TAVR. Using aggregate data from previous clinical trials,
multiple publications have demonstrated the additional advantages of Bayesian
re-analyses [@brophy; @goligher]. The current article suggests that similar
benefits may be observed when this approach is applied to individual patient
data in the context of an observational research design.

Our study also has limitations. First, actual individual data was unavailable,
which did not allow us to perform adjusted analysis with relevant covariates,
limiting appropriate confounding control. Yet, we note that the frequentist
results using extracted data from the reported Kaplan--Meier curve were very
similar to the original paper. Thus, it is unlikely that a Bayesian analysis
with actual individual data would yield highly different results compared to the
ones reported in the present article. Second, because we limited our analysis to
data extracted from Kaplan--Meier curves, we could only reanalyze the all-cause
mortality outcome. Third, these analyses were not preregistered; hence, they are
exploratory and should be interpreted with caution. Lastly, we limited our
analyses to a restricted number of priors and did not perform an extensive
sensitivity analyses regarding our Bayesian analyses.

In conclusion, while the original publication concluded there was "no difference in long-term survival between
patients who did and did not undergo permanent pacemaker implantation
after TAVR", this Bayesian reanalysis suggests a moderate to high probability that pacemaker implantation is associated with increased mortality in the first 4 years following TAVR.
<br>
<br>
<br>

\newpage

# References

<div id="refs"></div>

\newpage

# Table 1

<br><br>

```{r table1}
hr_table_fun = function(model, col_name){
  HR = 
    model |> 
    tidybayes::tidy_draws() |> 
    dplyr::summarise(HR = exp(treatPacemaker))
  
  colnames(HR) = col_name
  
  return(HR)
}

HRs = hr_table_fun(vague, "Vague") |> 
  dplyr::bind_cols(
    hr_table_fun(skeptical_model, "Skeptical"),
    hr_table_fun(informative, "Semi-informative SAVR 50%"),
    hr_table_fun(informative_100, "Fully-informative SAVR 100%"),
  ) |> 
  tidyr::pivot_longer(1:4)

HRcri95 = 
  HRs |> 
  dplyr::group_by(name) |> 
  ggdist::median_hdi(value) |> 
  dplyr::mutate(dplyr::across(value:.upper, ~round(.,2))) |> 
  dplyr::summarise("Belief" = name,
                   "HR (95% CrI)" = stringr::str_c(
                     value, " (", .lower, ", ", .upper, ")"))

HRsprobs = 
  HRs |> 
  dplyr::group_by(name) |> 
  dplyr::summarise("HR >1.00" = mean(value > 1),
                   "HR >1.10" = mean(value > 1.1),
                   "HR >1.25" = mean(value > 1.25)) |> 
  dplyr::mutate(dplyr::across(2:4, ~round(100*.,1))) |> 
  dplyr::rename("Belief" = name)

dplyr::left_join(HRcri95, HRsprobs) |> 
  dplyr::mutate(Belief = forcats::fct_rev(Belief)) |> 
  dplyr::arrange(Belief) |> 
  flextable::flextable() |> 
  flextable::autofit() |> 
  flextable::add_header_row(top = TRUE, 
                            values = c(" ", "Posterior probability, %"), 
                            colwidths = c(2, 3)) |> 
  flextable::theme_box()
```

```{r}
# Source: https://doi.org/10.1016/j.jclinepi.2019.10.015
# Section 4.2. Calculation of absolute effects for events (e.g., mortality)

RD_HR_fun = function(r0, HR){
  # r0 = baseline risk (no pacemaker group)
  # r1 = risk in the pacemaker group
  # HR = hazard ratio
  r1 = 1 - (1 - r0)^HR
  
  # RD = risk difference (%)
  100*(r1 - r0)
}

# Load digitalized data from KM curve on "No pacemaker" group

no_pace_data = read.csv(here::here("data/no_pacemaker_four_years_km.csv"),
                    header= TRUE)

# Extract risk at last time point 
baseline_risk = 
  
  # "100 -" is necessary because the original digitalized data regards "Cumulative Survival"
  # but we want the mortality risk
  # Thus, one needs to subtract 100 (%) by the survival value
  
  100 - no_pace_data[nrow(no_pace_data), 2]


rd_table_fun = function(model, col_name){
  rd = 
    model |> 
    tidybayes::tidy_draws() |> 
    dplyr::summarise(RD = RD_HR_fun(r0 = baseline_risk/100, HR = exp(treatPacemaker)))
  
  colnames(rd) = col_name
  
  return(rd)
}

RDs = rd_table_fun(vague, "Vague") |> 
  dplyr::bind_cols(
    rd_table_fun(skeptical_model, "Skeptical"),
    rd_table_fun(informative, "Semi-informative SAVR 50%"),
    rd_table_fun(informative_100, "Fully-informative SAVR 100%"),
  ) |> 
  tidyr::pivot_longer(1:4)

cri95 = 
  RDs |> 
  dplyr::group_by(name) |> 
  ggdist::median_hdi(value) |> 
  dplyr::mutate(dplyr::across(value:.upper, ~round(.,1))) |> 
  dplyr::summarise("Belief" = name,
                   "RD (95% CrI)" = stringr::str_c(
                     value, " (", .lower, ", ", .upper, ")"))

probs = 
  RDs |> 
  dplyr::group_by(name) |> 
  dplyr::summarise("RD >0%" = mean(value > 0),
                   "RD >1%" = mean(value > 1),
                   "RD >2%" = mean(value > 2)) |> 
  dplyr::mutate(dplyr::across(2:4, ~round(100*.,1))) |> 
  dplyr::rename("Belief" = name)

dplyr::left_join(cri95, probs) |> 
  dplyr::mutate(Belief = forcats::fct_rev(Belief)) |> 
  dplyr::arrange(Belief) |> 
  flextable::flextable() |> 
  flextable::autofit() |> 
  flextable::theme_box() |> 
  flextable::add_footer_lines('The assumed fixed baseline risk was 39.9%, based on the SWEDEHEART TAVR data on patients not exposed to pacemaker at 4 years.') |> 
  flextable::add_footer_lines('"Semi-informative SAVR 50%" regards posterior distribution while assuming a prior based on the surgical aortic valve replacement SWEDEHEART data with 50% of weight. "Fully-informative SAVR 100%" regards the same data, but with 100% weight.') |> 
  flextable::add_footer_lines('Abbreviations: HR, hazard ratio; RD, risk difference')
```


\newpage

# Figure Titles and Legends

Figure 1: Reconstructed Kaplan--Meier curve

This figure shows the reconstructed Kaplan--Meier all-cause mortality curve regarding the individual-patient data extracted from the propensity score-matched cohort. 

<br>

Figure 2: Difference in Survival Probability Across Time

This figure shows the difference in survival probabilities along with 95% confidence intervals (gray area) across time in years. A difference smaller than zero indicates
lower survival probability in patients exposed to pacemaker.

<br>

Figure 3: Prior and Posterior Distributions of the Hazard Ratio (4-year time window)

Underlying prior and marginal posterior distributions regarding analyses
restricted to 4-year time-window (Table 1). Panel A, Vague prior; B, Skeptical
prior ; C, Semi-informative prior “SAVR 50%”; D, Fully informative prior
“SAVR 100%”. Dashed lines depict the underlying prior distributions. Color
filled distributions represent the marginal posteriors. Interval bars depict the
median and 95% credible intervals of each marginal posterior distribution.
Colored filled areas depict the area under the curve above HR of 1.0, which
represents the posterior probability above 1.0. These probabilities are also
shown in each panel. In a similar manner, the probability of exceeding a HR
of 1.1 or 1.25 can be found by calculating the area under the curve to the right
of the vertical line at HR=1.1 and HR=1.25, respectively.


```{r fig3 helper function}
prior_vague = rstanarm::prior_summary(vague)
prior_skeptical = rstanarm::prior_summary(skeptical_model)
prior_informative50 = rstanarm::prior_summary(informative)
prior_informative100 = rstanarm::prior_summary(informative_100)

plot_fun = function(model, pp, y_end, color, xlab = F, ylab = F) {
  model |> 
  tidybayes::tidy_draws() |> 
  ggplot(aes(x = treatPacemaker,
             fill = stat(x > log(1)),
             slab_alpha = stat((x)))
         ) +
  # Only posterior with  ggdist::stat_halfeye()
  ggdist::stat_halfeye(# very important so all distributions are comparable
                       normalize = "none", 
                       fill_type = "gradient",
                       .width = 0.95, # 95% CrI
                       point_interval = ggdist::median_hdi
                       ) +
 # scale_slab_alpha_continuous(range = c(-0.2, 1.25)) +
  scale_fill_manual(values = c("gray80", color)) +
  
  # Prior 
  stat_function(fun = dnorm,
                args = c(mean = pp$priorEvent$location,
                         sd = pp$priorEvent$scale),
                alpha = 0.8,
                linetype = 2) +
  
  # Vertical line
  annotate(geom = "segment",
           x = log(1), y = 0,
           xend = log(1), yend = y_end) +
  
  scale_y_continuous(limits = c(0, 7),
                     breaks = seq(0, 6, 2),
                     expand = c(0, 0.4)) +
  scale_x_continuous(breaks = log(seq(0.8, 1.5, 0.1)),
                     limits = log(c(0.75, 1.55)),
                     labels = seq(0.8, 1.5, 0.1)) +
  labs(x = NULL,
       y = " ") +
  {if (xlab) labs(x = "Hazard Ratio (log scale)")} +   
  {if (ylab) labs(y = "Density")} + 
  ggdist::theme_ggdist() +
  theme(legend.position = 'none',
        plot.title.position = 'plot',
        plot.margin = margin(20, 20, 20, 20))
  
}
```

```{r fig3, include = FALSE}
pal = MetBrewer::met.brewer(name="Isfahan1",n=7,type="discrete")

p1 = plot_fun(vague, prior_vague,
              y_end = 2.5, color = pal[3],
              ylab = T) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[4, "HR >1.00"], "%"))


p2 = plot_fun(skeptical_model, prior_skeptical,
              y_end = 3.05, color = pal[2]) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[3, "HR >1.00"], "%"))

p3 = plot_fun(informative, prior_informative50,
              y_end = 1.5, color = pal[4],
              xlab = T, ylab = T) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[2, "HR >1.00"], "%"))

p4 = plot_fun(informative_100, prior_informative100,
              y_end = 0.65, color = pal[6],
              xlab = T) +
  annotate("text", x = log(1.4), y = 4.5,
           size = 5,
           label = paste(HRsprobs[1, "HR >1.00"], "%"))

# Suppress code used to save figure
# tiff(file = here::here("submissions", "IJC", "01_revision",
#                       'fig3.tif'),
#     type = "cairo", # to show the gradient from ggdist
#     height=12, width=20, units = "cm", res = 300)

p1 + p2 + p3 + p4 + patchwork::plot_annotation(tag_levels = "A")

# dev.off()
```

