---
title: "Untitled"
author: "Arthur M. Albuquerque"
date: "11/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

# Download rstanarm's "Survival Analysis Version" 
# https://github.com/stan-dev/rstanarm

# install.packages("rstanarm", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

library(rstanarm)
library(magrittr)
library(here)
```


```{r load data}
# load the 4-years digitalized KM datasets
load(here::here("output/data/both_ipd4.RData"))
```

# Vague prior

Fit model

```{r}
vague <- rstanarm::stan_surv(formula = survival::Surv(time, status) ~ 1  + treat,
                            data = both_ipd4,
                            chains  = 4,
                            cores = parallel::detectCores(),
                            seed  = 123,
                            warmup = 2000,
                            iter = 4000)

save(vague, file = here::here("output/fit/bayesian_model_vague.RData"))

```

Check priors

```{r}
rstanarm::prior_summary(vague)
```


Check baseline hazard posterior

```{r}
plot(vague)
```

Model summary

```{r}
print(vague, digits = 2)
```

HR 95% credible interval 

```{r}
vague %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::mean_qi(exp(treatPacemaker))
```


# Skeptical prior

```{r}
# Source: https://doi.org/10.1016/j.jcin.2018.11.008
# Table 4, "New pacemaker"

mean_prior = log(0.99)
se_prior = (log(1.49) - log(0.65))/3.92

skeptical_model =
  rstanarm::stan_surv(formula = survival::Surv(time, status) ~ 1 + treat,
                      prior = rstanarm::normal(mean_prior,se_prior), # coefficient
                      data = both_ipd4,
                      chains = 4,
                      cores = parallel::detectCores(),
                      seed = 123,
                      warmup = 2000,
                      iter = 4000)

save(skeptical_model, file = here::here("output/fit/bayesian_model_skeptical.RData"))
```

Check priors

```{r}
rstanarm::prior_summary(skeptical_model)
```

Check baseline hazard posterior

```{r}
plot(skeptical_model)
```

Model summary

```{r}
print(skeptical_model, digits = 2)
```

```{r}

skeptical_model %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::mean_qi(exp(treatPacemaker))
```


# Informative prior (50% SWEDEHEART SAVR)

```{r}
# informative prior hr 1.14; 95% CI, 1.01-1.29
# doi: 10.1001/jamanetworkopen.2021.16564

mean_prior = log(1.14)
se_prior = ((log(1.29) - log(1.01))/3.92) * 1.5 # downweight by 50%


informative <- rstanarm::stan_surv(formula = survival::Surv(time, status) ~ 1 + treat,
                            
                            prior = rstanarm::normal(mean_prior,se_prior), # coefficient
                            
                            data = both_ipd4,
                            chains = 4,
                            cores = parallel::detectCores(),
                            seed = 123,
                            warmup = 2000,
                            iter = 4000)

save(informative, file = here::here("output/fit/bayesian_model_informative.RData"))
```


Check priors

```{r}
rstanarm::prior_summary(informative)
```

Check baseline hazard posterior

```{r}
plot(informative)
```

Model summary

```{r}
print(informative, digits = 2)
```

```{r}

informative %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::mean_qi(exp(treatPacemaker))
```

# Informative prior (100% SWEDEHEART SAVR)

```{r}
# informative prior hr 1.14; 95% CI, 1.01-1.29
# doi: 10.1001/jamanetworkopen.2021.16564

mean_prior = log(1.14)
se_prior = ((log(1.29) - log(1.01))/3.92)


informative_100 <- rstanarm::stan_surv(formula = survival::Surv(time, status) ~ 1 + treat,
                            
                            prior = rstanarm::normal(mean_prior,se_prior), # coefficient
                            
                            data = both_ipd4,
                            chains = 4,
                            cores = parallel::detectCores(),
                            seed = 123,
                            warmup = 2000,
                            iter = 4000)

save(informative_100, file = here::here("output/fit/bayesian_model_informative_100.RData"))
```


Check priors

```{r}
rstanarm::prior_summary(informative_100)
```

Check baseline hazard posterior

```{r}
plot(informative_100)
```

Model summary

```{r}
print(informative_100, digits = 2)
```

```{r}

informative_100 %>% 
  tidybayes::tidy_draws() %>% 
  ggdist::mean_qi(exp(treatPacemaker))
```
